Kindly Bent to Free Us

### 2019-07-11 kindly/infer/infer.tex
Remove the TODOs.
Add an example for constraint solving.
Tighten everything a little bit.

An important contribution of \affe is its principal type inference.
We now formulate our inference algorithm
based on the $HM(X)$ framework~\citep{DBLP:journals/tapos/OderskySW99}.
$HM(X)$ is a Hindley-Milner type system for a language
with qualified types where constraints are expressed in an arbitrary
theory $X$.
Most important, given some properties on the constraint system $X$,
$HM(X)$ ensures principal type inference.
We apply HM(X) to a concrete constraint language which we name $\CL$.
We adapt and extend its existing rules to support kind inference,
track linearity and handle borrows and regions. Finally, we
formulate an appropriate constraint solving algorithm for $\CL$.
In addition, our constraint solving algorithm simplifies constraints in a
principled way.
We first present various preliminary definitions
before showing our kind and type inference judgements
and our constraint solving algorithm.

@@

In order to determine if a variable is used in an affine manner, we must track
its uses and the associated kinds. For instance, in the expression
$(x,x)$, $x$ is used twice. If $x$ is of type $\tau$, which is of kind $k$,
we must add the constraint $\Cleq{k}{\kun}$.
%
In order to infer such constraints, our inference judgement will not only
take an environment as parameter but also return an environment, which
we call ``usage environment'', and which summarize how variables and borrows
are used. Usage environments follow the exact same grammar
as normal environment. In order to distinguish them more easily,
we note them $\Sv$.

In \cref{sdtyping}, we used various relations to split environments in two, or
transform suspended bindings into borrow binding inside an environment.
These relations took as argument a constraint which is used to validate
the environment transformation.
In the context of inference, we define a new judgements which \emph{infers}
the constraints required.
\begin{itemize}
\item $\bsplit{C}{\Sv}{\bf{\Sv_1}}{\bf{\Sv_2}}$.
  Given two usage environments (inferred for two subexpressions, for instance)
  $\Sv_1$ and $\Sv_2$, we return $\Sv$, the merged environment, and $C$, a set
  of constraints that must be respected.
  This relation is total and non-ambiguous given $\Sv_1$ and $\Sv_2$
  and uses the same rules as the one presented in \cref{sdtyping:split}.
\item $\bregion{C}{\bf{x}}{\Sv}{\bf\Sv'}$.
  Given a usage environment $\Sv'$ and a variable name $x$, we return
  $\Sv$ where the borrow binding of $x$ in $\Sv'$, if it exists, is replaced by
  a suspended binding. We also return $C$, a set of constraints that must
  be respected.
  Again, the relation is total and non-ambiguous for any given $\Sv'$ and $x$,
  and uses the same rules as the one presented in \cref{sdtyping:regions}.
\end{itemize}

The relations used for syntax-directed typing can trivially be defined
in term of these new relations and constraint entailment.
All relations are fully described in \cref{typ:extra:envs}.

@@

The HM(X) framework assumes the existence of a $\operatorname{normalize}$
function which takes a constraint $C$ and a substitution $\psi$ and returns a
simplified constraint $C'$,
and an updated substitution $\unif'$.
Normalization is supposed to return the ``best'' solution $(C',\unif')$, for
instance the most general unifier.
We detail the implementation
of the normalization function and its property in \cref{infer:solving}.
In the meantime, we simply
assume the existence of such a function for our constraint system.

@@

We note $\inferK{(C,\unif)}{\bf{\E}}{\bf{\tau}}{k}$ when type $\tau$ has kind $k$
in environment $\E$ under constraints $C$ and unifier $\unif$.
$\E$ and $\tau$ are the input parameters of
our inference procedure.
We present the kind inference algorithm as a set of rules in
\cref{rules:kinding}.
Similar to the syntax-directed rules, higher-kinds are not generally supported
and can only appear by looking-up the kind scheme of a type constructor,
for use in the type application rule {\sc KApp}.
Type variables must be of a simple kind in rule {\sc KVar}.
Kind schemes are instantiated in the {\sc KVar} rules by creating
fresh kind variables and the associated substitution.
{\sc KArr} and {\sc KBorrow} simply returns the kind of the primitive
arrow and borrow types.
The $\operatorname{normalize}$ function is used every time several constraints
must be composed in order to simplify the constraint and return a most general
unifier.

@@

We note $\inferW{\Sv}{(C,\unif)}{\bf{\E}}{\bf{e}}{\tau}$ when
$e$\ has type $\tau$ in $\E$ under the constraints $C$ and unifier $\unif$
with a usage environment $\Sv$. $\E$ and $e$ are the input parameters of our
inference algorithm.
We revisit the syntax-directed rules presented in \cref{sdtyping} to highlight the
novelties
of our inference algorithm and the differences with the syntax-directed
system.
As before, the complete type inference rules are shown in \cref{appendix:infer}.

@@

In our syntax directed system presented in \cref{sdtyping}, we ensured
that linear variables are not discarded at the \emph{leafs}, through
the {\sc Var} rule. In the inference algorithm, we operate in the opposite
direction: we collect data from the leafs, and only enforce linearity
at \emph{binders}. This is reflected in the {\sc Var$_I$} and
{\sc Abs$_I$} rules presented in \cref{rule:infer:envs}.
Typing for variables is very similar to traditional (non-affine) ML
typing. The only difference is that we collect
the fact that $x$ was used with the scheme $\schm$ by returning
a usage environment $\Sv = \{ \bvar{x}{\schm} \}$.
%
This usage environment is in turn used at each binder to enforce proper
usage of linear variable via the $\Weaken$ property.
We demonstrate how this is achieved for lambda expressions
in the {\sc Abs$_I$} rule.
First, we typecheck the body of the lambda and obtain a usage
environment $\Sv_x$. Just like in the syntax directed,
we introduce the constraint
$\Cleq{\Sv\Sdel{x}}{\kvar}$ which properly accounts for captures in
the body of the lambda expression. We also introduce the constraint
$\Weaken_{\bvar{x}{\sigma}}(\Sv)$. If $x$ was used $e$, $x$ is present
in $\Sv$ and this constraint is empty. Otherwise, if $x$ is
\emph{not} present in $\Sv$, its type should not have a linear
kind, which is enforced by the constraints $\Cleq{\sigma}{\kaff_\infty}$.
The $\Weaken$ constraint is introduce at each binding point in the program
such as let-bindings and pattern matching.

Note again here the use of normalization on complex constraints to ensure
that the inference algorithm always return the simplest possible
constraints and unifiers.

@@

As noted previously, in our inference algorithm, we infer
usage environments which describes how variables are used. In
\cref{sdtyping}, we described the {\sc Pair} and {\sc Region} rules, and their
respective actions on the environment. We now see the inference version
of these rules in \cref{rule:infer:envrules}.
While the rules are quite similar to the original version, the usage
environment $\Sv$ is now an \emph{output} of the algorithm.
As such, we use the ``inference'' version of the relations on
environment,
$\bsplit{C}{\Sv}{\bf{\Sv_1}}{\bf{\Sv_2}}$ and $\bregion{C}{\bf{x}}{\Sv}{\bf\Sv'}$,
which returns the necessary constraints and
are total and non ambiguous for their input parameters ($\Sv_1, \Sv_2$ and $\Sv'$, respectively).
We then simply collect all the constraints and normalize them.

@@

So far, constraints have only been composed of a list of kind inequalities.
The internal language of constraints used for inference is in fact
richer.
To illustrate this, we now show the inference rule for let-bindings
in \cref{rule:infer:let}.
This rule combines several ingredients previously seen:
since let expressions are binders, we use $\Weaken$ on the bound
identifier $x$. Since let-expressions contain
two subexpressions, so we use the environment splitting relation,
$\bsplit{C_s}{\Sv}{\Sv_1}{(\Sv_2 \Sdel{x})}$. We carefully remove the $x$ from
the left environment, since it is not available outside of the expression
$e_2$, and thus should not be part of the returned usage environment.

@@

Before presenting our constraint solving algorithm,
we place ourselves in a more general context where kinds are either variables
or constants belonging to a total bounded lattice $(\mathcal L, \lk_\Lat)$ ie.,
a lattice which admits a total order and upper and lower bounds ($l^\top$ and $l^\bot$).
We note lattice elements $l$ and $\glb_i l_i$ (resp. $\lub_i l_i$)
the greatest lower bound (resp. least upper bound) in $\mathcal L$.
The lattice used in \lang which was presented
in \cref{sdtyping} is a total bounded lattice with
$l^\top = \klin_\infty$ and $l^\bot = \kun_0$.
%
Let $\CL$ the set of constraints in such arbitrary lattice $mathcal L$.
The full grammar of constraints is shown in \cref{grammar:constraint}.
Constraints are made of kind inequalities, conjunctions and
projections, as shown previously, along with type unification
constraints. Since types might contain kinds (for instance, on the arrows),
type unification is oriented and noted $\leq$.
For simplicity, we consider all type constructors
invariant in their parameters
and define $\Ceq{\tau}{\tau'}$ as $\Cleq{\tau}{\tau'} \wedge \Cleq{\tau'}{\tau}$.

@@

\TODO{Add example}

Our algorithm is complete, computes principal normal forms,
and already simplifies constraints significantly
(notably thanks to steps 6, 7 and 8).
It can be easily extended with further simplification phases.
In particular, our implementation and all the signatures presented in
\cref{motivation} use a variance-based simplification
where all covariant (resp. contravariant) variables are replaced by their
lower (resp. upper) bounds.
Remarkably, all the simplification mechanisms presented
here (including the variance-based one) are complete.
It is also possible to add ``best-effort'' simplification
rules which help reduce the size of inferred signatures even further
\citep{DBLP:conf/aplas/Simonet03}.
%
We now show that this algorithms is well-behaved with respect to entailment
and computes unique normal forms.

@@

The proofs are given in \cref{appendix:constraints}. These three properties
are sufficient to state that $HM(\CL)$ provides principal type inference.
However, we do not use HM(X) directly, but an extension with kind inference
and affine types and borrows.
We now show that HM(X)'s completeness and soundness theorems are still valid on
this extended system.

@@

\begin{theorem}[Completeness]
  Let $\inferS{C'}{\unif'\E}{e}{\schm'}$ a typing derivation,
  then $\inferW{\Sv}{(C,\unif)}{\Eflat\E}{e}{\tau}$
  for some substitution $\unif$, constraint $C$ and type $\tau$ such
  that
  \begin{align*}
    (C_\schm,\schm) &= \generalize{C}{\unif\E}{\tau}
    &\unif &\leq^{\phi}_{\fv{\E}} \unif'
    &\entail{C'&}{\phi C_\schm}
    &\entail{C'&}{\phi \schm \preceq \schm'}
    % &( C, \schm, \unif) &\leq (C',\schm',\unif')
  \end{align*}
\end{theorem}

>>>>

An important contribution of \affe is its principal type inference.
We now formulate our inference algorithm
based on the $HM(X)$ framework~\citep{DBLP:journals/tapos/OderskySW99}.
$HM(X)$ is a Hindley-Milner type system for a language
with qualified types where constraints are expressed in an arbitrary
theory $X$.
Most importantly,
$HM(X)$ ensures principal type inference
when $X$ respects the specified properties.
We apply HM(X) to a concrete constraint language which we name $\CL$.
We adapt and extend HM(X) existing rules to support kind inference,
track linearity and handle borrows and regions. Finally, we
formulate an appropriate constraint solving algorithm for $\CL$
which solves and simplifies constraints in a principled way.
We start by various preliminary definitions.

@@

In order to determine if a variable is used in an affine manner, we must track
its uses and the associated kinds. For instance, in the expression
$(x,x)$, $x$ is used twice. If $x$ is of type $\tau$, which is of kind $k$,
we must add the constraint $\Cleq{k}{\kun}$.
%
In order to infer such constraints, our inference judgement will not only
take an environment as parameter but also return an environment which
we call ``usage environment'' and which summarizes how variables and borrows
are used. Usage environments follow the exact same grammar
as normal environment. In order to distinguish them more easily,
we note them $\Sv$.

In \cref{sdtyping}, we used relations to split environments in two and to
transform suspended bindings into borrows inside a region.
These relations take as argument a constraint which validates
the transformations.
In the context of inference, we define new judgements which \emph{infers}
the constraints.
\begin{itemize}[leftmargin=*]
\item $\bsplit{C}{\Sv}{\bf{\Sv_1}}{\bf{\Sv_2}}$.
  Given two usage environments $\Sv_1$ and $\Sv_2$
  (inferred from two subexpressions, for instance),
  we return $\Sv$, the merged environment, and $C$, a set
  of constraints that must be respected.
  This relation is total and non-ambiguous given $\Sv_1$ and $\Sv_2$
  and uses the same rules as the one presented in \cref{sdtyping:split}.
\item $\bregion{C}{\bf{x}}{\Sv}{\bf\Sv'}$.
  Given a usage environment $\Sv'$ and a variable name $x$, we return
  $\Sv$ where the borrow binding of $x$ in $\Sv'$, if it exists, is replaced by
  a suspended binding. We also return $C$, a set of constraints that must
  be respected.
  Again, the relation is total and non-ambiguous for any given $\Sv'$ and $x$,
  and uses the same rules as the one presented in \cref{sdtyping:regions}.
\end{itemize}

The relations used for syntax-directed typing can trivially be defined
in term of these new relations by using constraint entailment.
All relations are fully described in \cref{typ:extra:envs}.

@@

The HM(X) framework assumes the existence of a $\operatorname{normalize}$
function which takes a constraint $C$, a substitution $\psi$ and returns a
simplified constraint $C'$
and an updated substitution $\unif'$.
Normalization must return a normal form such that $\unif'$ is a most general unifier.
We detail the implementation
of the normalization function and its property in \cref{infer:solving}.
In the meantime, we simply
assume the existence of such a function for our constraint system.

@@

We note $\inferK{(C,\unif)}{\bf{\E}}{\bf{\tau}}{k}$ when type $\tau$ has kind $k$
in environment $\E$ under constraints $C$ and unifier $\unif$.
$\E$ and $\tau$ are the input parameters of
our inference procedure.
We present the kind inference algorithm as a set of rules in
\cref{rules:kinding}.
Higher-kinds are not generally supported
and can only appear by looking-up the kind scheme of a type constructor,
for use in the type application rule {\sc KApp}.
Type variables must be of a simple kind in rule {\sc KVar}.
Kind schemes are instantiated in the {\sc KVar} rules by creating
fresh kind variables and the associated substitution.
{\sc KArr} and {\sc KBorrow} simply returns the kind of the primitive
arrow and borrow types.
The $\operatorname{normalize}$ function is used every time several constraints
must be composed in order to simplify the constraint and return a most general
unifier.

@@

We note $\inferW{\Sv}{(C,\unif)}{\bf{\E}}{\bf{e}}{\tau}$ when
$e$\ has type $\tau$ in $\E$ under the constraints $C$ and unifier $\unif$
with a usage environment $\Sv$. $\E$ and $e$ are the input parameters of our
inference algorithm.
Unlike in the syntax-directed version, $\E$ only regular and type bindings.
Suspended and borrow bindings can only be present in $\Sv$.
We revisit the syntax-directed rules presented in \cref{sdtyping} to highlight the
novelties
of our inference algorithm and the differences with the syntax-directed
system.
As before, the complete type inference rules are shown in \cref{appendix:infer}.

@@

In our syntax-directed system, we ensured
that linear variables are not discarded at the \emph{leafs}, through
the {\sc Var} rule. In the inference algorithm, we operate in the opposite
direction: we collect data from the leafs, and only enforce linearity
at \emph{binders}. This is reflected in the {\sc Var$_I$} and
{\sc Abs$_I$} rules presented in \cref{rule:infer:envs}.
Typing for variables is very similar to traditional (non-affine) ML
typing. The only difference is that we collect
the fact that $x$ was used with the scheme $\schm$ by returning
a usage environment $\Sv = \{ \bvar{x}{\schm} \}$.
%
This usage environment is in turn used at each binder to enforce proper
usage of linear variable via the $\Weaken$ property.
We demonstrate how this is achieved for lambda expressions
in the {\sc Abs$_I$} rule.
First, we typecheck the body of the lambda and obtain a usage
environment $\Sv_x$. Just like in the syntax directed,
we introduce the constraint
$\Cleq{\Sv\Sdel{x}}{\kvar}$ which properly accounts for captures in
the body of the lambda expression. We also introduce the constraint
$\Weaken_{\bvar{x}{\sigma}}(\Sv)$. If $x$ was used $e$, $x$ is present
in $\Sv$ and this constraint is empty. Otherwise, if $x$ is
\emph{not} present in $\Sv$, its type should not have a linear
kind, which is enforced by the constraints $\Cleq{\sigma}{\kaff_\infty}$.
The $\Weaken$ constraint is introduce at each binding point in the program
such as let-bindings and pattern matching.

Finally, we use normalization on complex constraints to ensure
that the inference algorithm always return the simplest possible
constraints and unifiers.

@@

We now present the inference version
of the {\sc Pair} and {\sc Region} rules in \cref{rule:infer:envrules}.
While the rules are quite similar to the original version, the usage
environment $\Sv$ is now an \emph{output} of the algorithm.
As such, we use the ``inference'' version of the relations on
environment,
$\bsplit{C}{\Sv}{\bf{\Sv_1}}{\bf{\Sv_2}}$ and $\bregion{C}{\bf{x}}{\Sv}{\bf\Sv'}$,
which return the necessary constraints.
As appropriate for inference, these relations 
are total and non ambiguous for their input parameters ($\Sv_1, \Sv_2$ and $\Sv'$, respectively).
We then collect all constraints and normalize them.

@@

So far, constraints have only been composed of a list of kind inequalities.
The internal language of constraints used for inference is in fact
richer.
To illustrate this, we show the inference rule for let-bindings
in \cref{rule:infer:let}.
This rule combines several ingredients previously seen:
since let expressions are binders, we use $\Weaken$ on the bound
identifier $x$. Since let-expressions contain
two subexpressions, we use the environment splitting relation,
$\bsplit{C_s}{\Sv}{\Sv_1}{(\Sv_2 \Sdel{x})}$. We remove the $x$ from
the right environment, since it is not available outside of the expression
$e_2$, and should not be part of the returned usage environment.

@@

We define the constraint solver in terms of an arbitrary bounded
lattice $(\mathcal L, \lk_\Lat)$, i.e., 
a lattice which has a minimal and a maximal element ($l^\top$ and $l^\bot$).
We write lattice elements as $l$ and $\glb_i l_i$ (resp. $\lub_i l_i$)
for the greatest lower bound (resp. least upper bound) in $\mathcal L$.
The lattice for \lang (see \cref{sdtyping}) is a bounded lattice with
$l^\top = \klin_\infty$ and $l^\bot = \kun_0$.

Let $\CL$ be the set of constraints in such a lattice $\mathcal L$.
The full grammar of constraints is shown in \cref{grammar:constraint}.
Constraints are made of kind inequalities, conjunctions and
projections, as shown previously, along with type unification
constraints. Since types might contain kinds (for instance, on the arrows),
type unification is oriented and noted $\leq$.
For simplicity, we consider all type constructors
invariant in their parameters
and define $\Ceq{\tau}{\tau'}$ as $\Cleq{\tau}{\tau'} \wedge \Cleq{\tau'}{\tau}$.

@@

An example of this algorithm in action is shown in \cref{solving:example}.
Our algorithm is complete, computes principal normal forms,
and already simplifies constraints significantly
(thanks to steps 6, 7 and 8).
It can be extended with further simplification phases.
In particular, our implementation and all the signatures presented in
\cref{motivation} use a variance-based simplification
where all covariant (resp. contravariant) variables are replaced by their
lower (resp. upper) bounds.
All the simplification mechanisms presented
here, including the variance-based one, are complete.
It is also possible to add ``best-effort'' simplification
rules which help reduce the size of inferred signatures even further
\citep{DBLP:conf/aplas/Simonet03}.
%
We now show that this algorithms is well-behaved with respect to entailment
and computes unique normal forms.

@@

The proofs are given in \cref{appendix:constraints}. These three properties
are sufficient to state that $HM(\CL)$ provides principal type inference.
However, we use an extension of HM(X) with kind inference
and affine types and borrows.
We now show that HM(X)'s completeness and soundness theorems are still valid on
this extended system.

@@

\begin{theorem}[Completeness]
  Given $\inferS{C'}{\E'}{e}{\tau'}$ and
  $\entail{}{\unif'\E \preceq \E'}$.
  Then $$\inferW{\Sv}{(C,\unif)}{\Eflat\E}{e}{\tau}$$
  for some environment $\Sv$,
  substitution $\unif$, constraint $C$ and type $\tau$ such
  that
  \begin{align*}
    \unif &\leq^{\phi}_{\fv{\E}} \unif'
    &\entail{C'&}{\phi C}
    &\entail{&}{\phi \schm \preceq \schm'}
    &\Sv&\subset\E
    % &( C, \schm, \unif) &\leq (C',\schm',\unif')
  \end{align*}
  where $\schm' = \generalize{C'}{\E'}{\tau'}$
  and $\schm = \generalize{C}{\E}{\tau}$
\end{theorem}

### 2019-07-11 kindly/intro.tex
Tighten everything a little bit.

Most type systems provide just type soundness, but neglect the
protocol aspect. The systems that do build on linear types \cite{DBLP:journals/tcs/Girard87} and/or
uniqueness types\cite{DBLP:conf/plilp/BarendsenS95}. A value of linear
type is guaranteed to be consumed 
exactly once. That is, a file that has been opened must be closed and
memory that has been allocated must be released. A value of unique
type is guaranteed to have a single reference to it.

@@

The concepts of ownership and borrowing have grown popular over time
and they form the foundation of the type system of the Rust language
\cite{rust}. Rust supports two kinds of borrows of data structures, mutable and immutable
ones. Mutable borrows enable modification of the data structure
whereas immutable borrows grant read-only access. Mutable borrows are
exclusive whereas several immutable borrows can be active at the same
time. Moreover, Rust makes sure that the lifetime of a
borrow is properly contained in the lifetime of its lender.

@@

\begin{itemize}
\item A type system that encodes linearity and affinity with
  borrowing. The type system is polymorphic with respect to types as
  well as kinds that express constraints on the number of uses of a value.
\item An extension of the HM(X) framework
  \cite{DBLP:journals/tapos/OderskySW99} with kinds, regions, and
  multiplicity constraints that supports full, prinicipal type
  inference.
\item Full account of the metatheory for type inference and type soundness.
\item Constraint simplification techniques.
\item Automatic inference of regions for borrows.
\item An implementation of the type inference algorithm including all
  constraint simplification and extended with pattern matching. A
  webfront for the algorithm is available, its URL is given in the
  non-anonymous supplementary material, and we plan to submit it for
  artifact evaluation.
\end{itemize}

>>>>

Most type systems provide just type soundness, but neglect the
protocol aspect. The systems that do build on linear types \cite{DBLP:journals/tcs/Girard87} and/or
uniqueness types~\cite{DBLP:conf/plilp/BarendsenS95}. A value of linear
type is guaranteed to be consumed 
exactly once. That is, a file that has been opened must be closed and
memory that has been allocated must be released. A value of unique
type is guaranteed to have a single reference to it.

@@

The concepts of ownership and borrowing have grown popular over time
and they form the foundation of the type system of the Rust language
\cite{rust}. Rust supports two kinds of borrows of data structures, shared and
exclusive ones.
Exclusive borrows generally enable modification of the data structure
whereas shared borrows only grant read-only access.
Several shared borrows can be active at the same time, but
can not be active while an exclusive borrow is.
Moreover, Rust makes sure that the lifetime of a
borrow is properly contained in the lifetime of its lender.

@@

\begin{itemize}
\item A type system that encodes linearity and affinity with
  borrowing. The type system is polymorphic with respect to types as
  well as kinds that express constraints on the number of uses of a value.
\item An extension of the HM(X) framework
  \cite{DBLP:journals/tapos/OderskySW99} with kinds, regions, and
  multiplicity constraints that supports full, principal type inference.
\item Full account of the metatheory for type inference and type soundness.
\item Constraint simplification techniques.
\item Automatic inference of regions for borrows.
\item An implementation of the type inference algorithm including all
  constraint simplification and extended with pattern matching. A
  webfront for the algorithm is available, its URL is given in the
  non-anonymous supplementary material, and we plan to submit it for
  artifact evaluation.
\end{itemize}

### 2019-07-11 kindly/lang.tex
Tighten everything a little bit.

\lstMakeShortInline[style=rule,columns=flexible,basicstyle=\normalsize\normalfont]@

@@

Addresses $\Addr$ are composed of a raw location $\Loc$, which is just
a pointer into a store, and a stack of modifiers that indicates the
borrows that have been taken from the original object. From the raw
location, we may take affine borrows and reborrowed. Once we have
taken an unrestricted borrow (from a raw location or a borrowed one),
then we can take further unrestricted borrows from it, but no more
affine ones.

@@

Finally, the store $\Store$ is a mapping from raw locations to
storables. It comes with a function
@salloc : store -> storable -> (loc * store)@ such that
@salloc delta w@ allocates a free location in @delta@ and fills it with
storable $w$. It returns the location and the updated store.

@@

We give some excerpts of the definition of @eval@ in
\cref{fig:big-step-interpretation} and leave the full 
definition for the appendix~\cref{sec:semant-defin}. The appendix also
contains the semantics 
in traditional notation, which does not make the monadic nature of
evaluation explicit.

>>>>

\lstMakeShortInline[style=rule,basicstyle=\normalsize\normalfont]@

@@

Addresses $\Addr$ are composed of a raw location $\Loc$, which is just
a pointer into a store, and a stack of modifiers that indicates the
borrows that have been taken from the original object. From the raw
location, we may take affine borrows and reborrows. Once we have
taken an unrestricted borrow (from a raw location or a borrowed one),
then we can take further unrestricted borrows from it, but no more
affine ones.

@@

Finally, the store $\Store$ is a mapping from raw locations to
storables. It comes with a function
@salloc@ of type @store -> storable -> (loc * store)@ such that
@salloc delta@ @w@ allocates a free location in @delta@ and fills it with
storable $w$. It returns the location and the updated store.

@@

We give some excerpts of the definition of @eval@ in
\cref{fig:big-step-interpretation} and leave the full 
definition for \cref{sec:semant-defin}. The appendix also
contains the semantics 
in traditional notation, which does not make the monadic nature of
evaluation explicit.
